Classical Simulation of Quantum Error Correction in a Fibonacci Anyon Code

### 2015-09-07 fib2.tex
first pass at addressing ref A's comments

Typical thermal noise processes in this kind of system are 
pair-creation, hopping, exchange etc.~of anyons. Such a model was analyzed in detail for Ising anyons in Ref.~\cite{Brell2013}.
It was seen that a simplified noise model consisting of pair-creation events only 
is sufficient to capture the qualitative features of an error-correction simulation, and so for convenience we 
will restrict to pair-creation noise processes in the numerical results presented in this study.

@@

\begin{figure}[t!]
\begin{center}
	\includegraphics[width=\columnwidth]{anyons-kyle.pdf}
\caption{The decoder failure rate (a lower bound on the logical error probability) is shown as a function of simulation time for linear lattice sizes from $L=16$ to $128$. 
This exhibits threshold behavior at a critical memory lifetime of $t_{\mathrm{sim}}^*\simeq 0.125$. 
This implies the Fibonacci anyon code simulated here is able to perfectly reliably store quantum information for times less than $t_{\mathrm{sim}}^*$ in the $L\to \infty$ limit.}
\label{f:threshold}
\end{center}
\vspace{-10pt}
\end{figure}

We can guarantee that error-correction will succeed whenever
the action of noise plus decoder 
does not percolate the anyons over the lattice,
but it is possible that percolated events may still result in no error. 
The connection between the percolation threshold and the error-correction threshold 
is not well understood in general~\cite{Hastings2014}, though it is clear 
that our threshold estimate will be a lower bound for 
the true threshold that may be found if all events 
(including those that have percolated) were simulated. 
However, calculations of homologically nontrivial operations for small lattice sizes suggest that almost all such 
processes will indeed either cause a logical error or a complete failure to return to the codespace.
As such we expect that neglecting the full simulation of 
these events does not significantly affect our observed threshold value.

>>>>

Typical thermal noise processes in this kind of system are 
pair-creation, hopping, exchange etc.~of anyons. Such a model was analyzed in detail for Ising anyons in Ref.~\cite{Brell2013}.
For convenience, in the numerical results presented in this study we will restrict to a simplified noise model consisting of pair-creation events only, though all of our simulation techniques could be applied directly to the more general families of noise models considered in Ref.~\cite{Brell2013} as desired. It was seen in Ref.~\cite{Brell2013} that the pair-creation-only setting was sufficient to capture the qualitative features of an error-correction simulation for the Ising anyons and we have no reason to expect that this would change when considering the Fibonacci anyon model.

@@

\begin{figure}[t!]
\begin{center}
	\includegraphics[width=\columnwidth]{anyons-kyle.pdf}
\caption{The decoder failure rate (a lower bound on the logical error probability) is shown as a function of simulation time for linear lattice sizes from $L=16$ to $128$. 
This provides strong evidence of threshold behavior at a critical memory lifetime of $t_{\mathrm{sim}}^*\simeq 0.125$. 
The existence of such a threshold implies that the Fibonacci anyon code simulated here is able to perfectly reliably store quantum information for times less than $t_{\mathrm{sim}}^*$ in the $L\to \infty$ limit. \cggb{Is this hedged enough? Maybe replace ``implies'' with ``would imply''?}}
\label{f:threshold}
\end{center}
\vspace{-10pt}
\end{figure}

We can guarantee that error-correction will succeed whenever
the action of noise plus decoder 
does not percolate the anyons over the lattice,
but it is possible that percolated events may still result in no error. 
The connection between the percolation threshold and the error-correction threshold 
is not well understood in general~\cite{Hastings2014}, though it is clear 
that our threshold estimate will be a lower bound for 
the true threshold that may be found if all events 
(including those that have percolated) were simulated. 
However, calculations of homologically nontrivial operations for small lattice sizes suggest that almost all such 
processes will indeed either cause a logical error or a complete failure to return to the codespace.
\cggb{Some kind of graph here to address Ref.~A's comment 3?}
As such we expect that neglecting the full simulation of 
these events does not significantly affect our observed threshold value.
